### 2019-12-17 doe_report_dec_2019/doe_2019_report.tex
Adding locations for conference talks.

\section*{Run Coordinating}
I stepped down from run coordinator in March, 2019. The POT-weighted detector uptime when I was on duty is 99.02\% for Far Detector and 98.47\% for Near Detector.

@@

\section*{Leading the DDT Group}
I have been serving as the DDT convener since May, 2019. I have held meetings for summer work, supporting the DAQ and operations groups, and talking about new trigger ideas from the exotics group.

@@

\section*{Conference Talks}
\begin{itemize}
  \item APS April Meeting 2019, April 15, 2019 \\
        $\nu_\mu$ Charged-Current Inclusive Cross-Section Measurement in the NOvA Near Detector
  \item SUSY2019, May 21, 2019 \\
        Neutrino Cross-Section Measurements in the NOvA Near Detector at Fermilab
\end{itemize}

>>>>

\section*{Leadership}
\begin{itemize}
  \item \textbf{Run Coordinating} I stepped down from run coordinator in March, 2019. The POT-weighted detector uptime when I was on duty is 99.02\% for Far Detector and 98.47\% for Near Detector.
  \item \textbf{A Committee Member of the Cross Section Tuning Paper}
  \item \textbf{Leading the DDT Group} I have been serving as the DDT convener since May, 2019. I have held meetings for summer work, supporting the DAQ and operations groups, and talking about new trigger ideas from the exotics group.
\end{itemize}

@@

%\section*{Leading the DDT Group}

@@

\section*{Conference Talks}
\begin{itemize}
  \item APS April Meeting 2019, April 15, 2019 @ Denver, Colorado\\
        $\nu_\mu$ Charged-Current Inclusive Cross-Section Measurement in the NOvA Near Detector
  \item SUSY2019, May 21, 2019 @ Corpus Christi, Texas\\
        Neutrino Cross-Section Measurements in the NOvA Near Detector at Fermilab
\end{itemize}
